### 2016-07-17 version0.0/paper1.tex
fig.s and table corrections

The first attempt at scaling the star formation rate was to find a relation between the total star formation rate (SFR) and the mass of interstellar gas. \citet{Schmidt59} proposed a power-law relation between SFR and the gas mass ($M_{\rm gas}$) with {\it N} as the power law exponent. Since then, for more than 50 years empirical star formation laws (relations) have been investigated using both observational data and numerical simulations. Later, \citet{Kennicutt98a} examined H$\alpha$, H\,{\sc I}, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies. He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with a power-law exponent of $1.4 \pm 0.15$. Using this power-law index, the Schmidt law can be rewritten as:

@@

Furthermore, the range of power-law indices calculated for the Andromeda galaxy using the K-S law is between 0.5 and 2 \citep[e.g.][]{Tabatabaei10,Ford13}. The use of different methods and data results in measuring different values for the power-law index. In a recent study of the K-S law in M31, \citet{Ford13} tested this law on six annular regions using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus H\,{\sc I}, and total gas calculated from dust emission). The measured power-law indices for each map and region vary between 0.6 to 2.03. The origin of these variations in the results is still an open question. It is unclear whether it depends on galactocentric distance, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law not working in M31. In order to examine the dependence of the results on the fitting method, we also applied a new statistical method, instead of the Ordinary Least Squares (OLS) fitting which is more commonly used in the literature to test the K-S law ($\S$~\ref{sec:fitting}).

@@

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\sc I}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\sun$.

In this project we used values based on the Kroupa IMF as is standard in the field, although discussion continues on whether the IMF is universal \citep{Bastin10}. Where necessary we converted from calibration values based on the Salpeter IMF by multiplying by 0.67  \citep{Madau14}.

@@

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\rm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\rm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\rm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3\% of the pixels within a 25 kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

\begin{figure*}
    \centering
       \includegraphics[width=164mm]{../image_paper1/sfr_fir.eps}
    \caption {SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}). The SFR map here has an angular resolution of 18\arcsec and pixel size of 9.85\arcsec, the same as the MIPS 70 $\mu$m map.}
    \label{fig:sfrs}
\end{figure*}

@@

The SFR can also be calculated using a combination of \halpha and \Spitzer  24 \um maps. \halpha emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha emission is very sensitive to dust extinction. Therefore, the combination of the \halpha and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\rm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

\citet{Calzetti07} introduced a new calibration using the same bandpasses for the case of local regions:
\begin{equation}
\label{equ: halphaplus24_l}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)],
\end{equation}
\noindent where the units here are the same as in equation~\ref{equ: halphaplus24_g}. Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc and is what we used for testing the SFR laws in local regions. The total M31 SFR calculated from summing pixel values and applying equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.

@@

Total infrared luminosity can be measured from the integration of the infrared part of a galaxy's spectral energy distribution or by combining photometric data at different IR wavelengths. As an example of the second approach, \citet{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity. \citet{Boquien10} tested and modified this calibration as:
\begin{equation}
 \label{equ: TIR}
L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160),
\end{equation}
\noindent where L(8), L(24), L(70), and L(160) are the luminosities of the galaxy at 8 $\mu$m, 24~$\mu$m, 70~$\mu$m, and 160~\um in units of erg~s$^{-1}$. We used results from equation~\ref{equ: TIR} in the equation~\ref{equ:sfr_fir} to calculate our final map of the M31 SFR (Figure~\ref{fig:sfrs}). Using this method, we calculated the total SFR by adding all the pixels to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$. Table~\ref{table:sfr} compares recent measurements of the total SFR of M31 from the literature and the present work.

\begin{table*}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24~$\mu$m&0.31 \\
Current work&\halpha and 24~$\mu$m&0.35 \\
Current work&TIR luminosity&0.4\\
\citet{Ford13}&FUV and 24~$\mu$m&0.25\\
\citet{Ford13}&TIR luminosity&0.48-0.52\\
\citet{Azimlu11}& \halpha and 24~$\mu$m&0.34\\
\citet{Azimlu11}&Extinction-corrected \halpha&0.44\\
\citet{Tabatabaei10}&Extinction-corrected \halpha&0.27--0.38\\
\citet{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table*}

@@

The molecular form of hydrogen is very difficult to detect. Therefore, CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][]{Sanders84}. Higher rotational transitions of CO can be used as tracers as well; however, they are not as common as $J(1\rightarrow 0)$. Equation~\ref{equ:conversion} shows the relation between CO emission and H$_2$ column density:
\begin{equation}
\label{equ:conversion}
\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/[{\rm K km s^{-1}}],
\end{equation}
\noindent where X$_{CO}$ is the conversion factor (also known as the X-factor), I$_{CO}$ is the CO intensity in  K~km~s$^{-1}$ and N$_{H_2}$ is the molecular hydrogen column density. The X-factor could be different in regions within a galaxy due to varying metallicity \citep{Wilson95, Bosselli02, Bolato13}. In the case of M31, different values of X-factor in the range of ($1-5.6 \times 10^{20}$) were adopted in previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant difference in X-factor leads to horizontal changes in a plot of log(SFR) versus log($\Sigma_{\rm {gas}}$) and does not affect our power-law indices for molecular gas, we chose $X_{\rm {CO}}= 2 \times 10^{20}$. This is the same value that is adopted in many other works \citep[e.g.][]{Ford13, Smith12}. Since H\,{\sc I} mass dominates over the H$_2$ mass in M31, the constant X-factor has a negligible effect on the total gas mass.

@@

The total gas mass was calculated from:
\begin{equation}
\label{equ:total_gas}
\rm M_{\rm \bld {total \, gas}} = 1.36[M_{\rm H I}+M_{H_2}],
\end{equation}
\noindent where the factor of 1.36 is a constant that takes into account the contribution of He and other heavier elements to the total gas mass, M$_{\rm H\,{\sc I}}$ is the mass of neutral hydrogen that was obtained from 21 cm observations (the map, which we got from \citet{Chemin09}, has units of number density which we used to calculate mass density of H\,{\sc I}), and M$_{H_2}$ was calculated from equation~\ref{equ:conversion} in units of M$_{\sun}$/pc$^2$. We assumed a gas mass of zero for regions where data for  either M$_{\rm H\,{\sc I}}$ or M$_{H_2}$ was not available, due to differences in coverage or bad pixels, etc. In this case the above equation gives a lower limit for the total gas; this applies to regions beyond 18~kpc from the galaxy centre.

%----------------------------------------------------------------------------------------
%STELLAR MASS
%----------------------------------------------------------------------------------------
\subsection{Stellar Mass}
\label{sec:starmass}
\begin{figure*}
\centering
\includegraphics[width=164mm]{../image_paper1/star.eps}.
\caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
\label{fig:stellarmass}
\end{figure*}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ:eskew}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in the aforementioned paper. 
Figure~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8\% of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1\%.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6\%. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56\% of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.

@@

The metallicity of a galaxy can be estimated by measuring abundances of heavier elements in its ISM. 
It is common to use  gas phase oxygen abundance, $[{\rm O/H}]$, as a gauge to determine metallicity \citep[e.g.][]{McGaugh91, Zaritsky94}. 
Results from modelling dust in the Milky Way and nearby galaxies showed that the dust to gas mass ratio depends on $[{\rm O/H}]$ and, consequently, on metallicity \citet{Draine07}. \citet{Draine14} assumed that depletion of gas elements from the gas to the diffuse ISM in M31 is similar to the Milky Way, and proposed that: 
 \begin{equation}
 \label{equ: metal}
\frac{M_d}{M_H}=0.0091 \frac{Z}{Z_{\odot}},
 \end{equation} 
\noindent where M$_d$ and M$_H$ are the total masses of dust and hydrogen, $Z$ is the metallicity of M31 and $Z_{\odot}$ is solar metallicity.

>>>>

The first attempt at scaling the star formation rate was to find a relation between the total star formation rate (SFR) and the mass of interstellar gas. \citet{Schmidt59} proposed a power-law relation between SFR and the gas mass ($M_{\mathrm gas}$) with {\it N} as the power law exponent. Since then, for more than 50 years empirical star formation laws (relations) have been investigated using both observational data and numerical simulations. Later, \citet{Kennicutt98a} examined H$\alpha$, H\,{\textsc i}, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies. He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with a power-law exponent of $1.4 \pm 0.15$. Using this power-law index, the Schmidt law can be rewritten as:

@@

Furthermore, the range of power-law indices calculated for the Andromeda galaxy using the K-S law is between 0.5 and 2 \citep[e.g.][]{Tabatabaei10,Ford13}. The use of different methods and data results in measuring different values for the power-law index. In a recent study of the K-S law in M31, \citet{Ford13} tested this law on six annular regions using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus H\,{\textsc i}, and total gas calculated from dust emission). The measured power-law indices for each map and region vary between 0.6 to 2.03. The origin of these variations in the results is still an open question. It is unclear whether it depends on galactocentric distance, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law not working in M31. In order to examine the dependence of the results on the fitting method, we also applied a new statistical method, instead of the Ordinary Least Squares (OLS) fitting which is more commonly used in the literature to test the K-S law ($\S$~\ref{sec:fitting}).

@@

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\textsc i}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.

In this project we used values based on the Kroupa IMF as is standard in the field, although discussion continues on whether the IMF is universal \citep{Bastin10}. Where necessary we converted from calibration values based on the Salpeter IMF by multiplying by 0.67~\citep{Madau14}.

@@

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\mathrm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3 per cent of the pixels within a 25~kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

\begin{figure}
    \centering
       \includegraphics[width=\textwidth]{../image_paper1/sfr_fir.eps}
    \caption {SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}). The SFR map here has an angular resolution of 18\arcsec and pixel size of 9.85\arcsec, the same as the MIPS 70 $\mu$m map.}
    \label{fig:sfrs}
\end{figure}

@@

The SFR can also be calculated using a combination of \halpha and \Spitzer  24 \um maps. \halpha emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha emission is very sensitive to dust extinction. Therefore, the combination of the \halpha and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\mathrm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

\citet{Calzetti07} introduced a new calibration using the same bandpasses for the case of local regions:
\begin{equation}
\label{equ: halphaplus24_l}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)],
\end{equation}
\noindent where the units here are the same as in equation~\ref{equ: halphaplus24_g}. Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc and is what we used for testing the SFR laws in local regions. The total M31 SFR calculated from summing pixel values and applying equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\odot$~yr$^{-1}$, which is in good agreement with previous studies.

@@

Total infrared luminosity can be measured from the integration of the infrared part of a galaxy's spectral energy distribution or by combining photometric data at different IR wavelengths. As an example of the second approach, \citet{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity. \citet{Boquien10} tested and modified this calibration as:
\begin{equation}
 \label{equ: TIR}
L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160),
\end{equation}
\noindent where L(8), L(24), L(70), and L(160) are the luminosities of the galaxy at 8 $\mu$m, 24~$\mu$m, 70~$\mu$m, and 160~\um in units of erg~s$^{-1}$. We used results from equation~\ref{equ: TIR} in the equation~\ref{equ:sfr_fir} to calculate our final map of the M31 SFR (Fig.~\ref{fig:sfrs}). Using this method, we calculated the total SFR by adding all the pixels to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$. Table~\ref{table:sfr} compares recent measurements of the total SFR of M31 from the literature and the present work.

\begin{table}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24~$\mu$m&0.31 \\
Current work&\halpha and 24~$\mu$m&0.35 \\
Current work&TIR luminosity&0.4\\
\citet{Ford13}&FUV and 24~$\mu$m&0.25\\
\citet{Ford13}&TIR luminosity&0.48-0.52\\
\citet{Azimlu11}& \halpha and 24~$\mu$m&0.34\\
\citet{Azimlu11}&Extinction-corrected \halpha&0.44\\
\citet{Tabatabaei10}&Extinction-corrected \halpha&0.27--0.38\\
\citet{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table}

@@

The molecular form of hydrogen is very difficult to detect. Therefore, CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][]{Sanders84}. Higher rotational transitions of CO can be used as tracers as well; however, they are not as common as $J(1\rightarrow 0)$. Equation~\ref{equ:conversion} shows the relation between CO emission and H$_2$ column density:
\begin{equation}
\label{equ:conversion}
\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/[{\mathrm K km s^{-1}}],
\end{equation}
\noindent where X$_{CO}$ is the conversion factor (also known as the X-factor), I$_{CO}$ is the CO intensity in  K~km~s$^{-1}$ and N$_{H_2}$ is the molecular hydrogen column density. The X-factor could be different in regions within a galaxy due to varying metallicity \citep{Wilson95, Bosselli02, Bolato13}. In the case of M31, different values of X-factor in the range of ($1-5.6 \times 10^{20}$) were adopted in previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant difference in X-factor leads to horizontal changes in a plot of log(SFR) versus log($\Sigma_{\mathrm {gas}}$) and does not affect our power-law indices for molecular gas, we chose $X_{\mathrm {CO}}= 2 \times 10^{20}$. This is the same value that is adopted in many other works \citep[e.g.][]{Ford13, Smith12}. Since H\,{\textsc i} mass dominates over the H$_2$ mass in M31, the constant X-factor has a negligible effect on the total gas mass.

@@

The total gas mass was calculated from:
\begin{equation}
\label{equ:total_gas}
\rm M_{\mathrm{total \, gas}} = 1.36[M_{\mathrm H I}+M_{H_2}],
\end{equation}
\noindent where the factor of 1.36 is a constant that takes into account the contribution of He and other heavier elements to the total gas mass, M$_{\mathrm H\,{\textsc i}}$ is the mass of neutral hydrogen that was obtained from 21 cm observations (the map, which we got from \citet{Chemin09}, has units of number density which we used to calculate mass density of H\,{\textsc i}), and M$_{H_2}$ was calculated from equation~\ref{equ:conversion} in units of M$_{\odot}$pc$^{-2}$. We assumed a gas mass of zero for regions where data for  either M$_{\mathrm H\,{\textsc i}}$ or M$_{H_2}$ was not available, due to differences in coverage or bad pixels, etc. In this case the above equation gives a lower limit for the total gas; this applies to regions beyond 18~kpc from the galaxy centre.

%----------------------------------------------------------------------------------------
%STELLAR MASS
%----------------------------------------------------------------------------------------
\subsection{Stellar Mass}
\label{sec:starmass}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_paper1/star.eps}
\caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
\label{fig:stellarmass}
\end{figure}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ:eskew}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in the aforementioned paper. 
Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8 per cent of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1 per cent.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6 per cent. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56 per cent of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.

@@

The metallicity of a galaxy can be estimated by measuring abundances of heavier elements in its ISM. 
It is common to use  gas phase oxygen abundance, $[{\mathrm O/H}]$, as a gauge to determine metallicity \citep[e.g.][]{McGaugh91, Zaritsky94}. 
Results from modelling dust in the Milky Way and nearby galaxies showed that the dust to gas mass ratio depends on $[{\mathrm O/H}]$ and, consequently, on metallicity \citet{Draine07}. \citet{Draine14} assumed that depletion of gas elements from the gas to the diffuse ISM in M31 is similar to the Milky Way, and proposed that: 
 \begin{equation}
 \label{equ: metal}
\frac{M_d}{M_H}=0.0091 \frac{Z}{Z_{\odot}},
 \end{equation} 
\noindent where M$_d$ and M$_H$ are the total masses of dust and hydrogen, $Z$ is the metallicity of M31 and $Z_{\odot}$ is solar metallicity.

\citet{Draine14} produced two dust maps of M31 using MIPS-160 resolution (FWHM  39\arcsec; 18\arcsec $\times$ 18\arcsec pixels) and SPIRE 350 resolution (FWHM 24\arcsec.9; 10\arcsec $\times$ 10\arcsec pixels), which are publicly available. 
We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\textsc i} map, then divided this dust mass by the mass of hydrogen in M31. 
However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citet{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2. We divided our dust map by 2 to account for this correction. 
We then generated a metallicity map of M31 by using the dust map in combination with equation~\ref{equ: metal}. \citet{Draine14} showed that with increasing distance from the centre of M31, the dust to H mass ratio declines monotonically and concluded that metallicity also behaves in the same way. 
Their fitting results showed that M31 can be divided into three regions ($R< 8~\kpc$, $8~\kpc < R < 18~\kpc$, and $18~\kpc < R < 25~\kpc$) where the dust to H mass ratio (or metallicity) has a different correlation with galactocentric distance.
